Notes on the low density parameters in {\tt MAESTRO}

### 2008-06-20 docs/lo_density/paper.tex
New global variables stored in geometry.f90: "base_cutoff_density_coord" and "burning_cutoff_density_coord".  We need coordinates so we can sync up how these affect the problem at all levels of refinement.  Just using a real number sometimes led to dynamics on fine grids being different from coarse grids right at the cutoff locations - in particular when the "higher" of two fine cells on top of a coarse cell was considered above the cutoff and the "lower" of the two fine cells was considered below the cutoff.  We compute the coordinaet locations at the same time we compute the anelastic_cutoff

These are working notes for the low density parameters in {\tt MAESTRO}.
\section{anelastic\_cutoff}
\begin{itemize}
\item In {\tt base\_state}, we abort the program if {\tt anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.
\item After we initilize the base state in {\tt varden} and at the beginning of {\tt advance}, We compute the coordinate associated with {\tt anelastic\_cutoff}, {\tt anelastic\_cutoff\_coord}.  This is done by setting ${\tt anelastic\_cutoff\_coord}= r$ as soon as $\rho_0(r) <$ {\tt anelastic\_cutoff}.
\item In {\tt correct\_base}, we only update $\rho_0$ for $r\in[0,{\tt anelastic\_cutoff\_coord}-1]$.
\item In {\tt make\_div\_coeff}, we change how we compute {\tt div\_coeff} at and above ${\tt anelastic\_cutoff\_coord}$.
\item In {\tt make\_psi}, we only compute $\psi$ for $r\in[0,{\tt anelastic\_cutoff\_coord}-1]$.
\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} to zero at and above ${\tt anelastic\_cutoff\_coord}$.
\end{itemize}
\section{base\_cutoff\_density}
\begin{itemize}
\item In {\tt base\_state}, we abort the program if {\tt anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.
\item In {\tt base\_state}, we compute a physical cutoff location, {\tt base\_cutoff\_density\_loc}, which is defined as the physical location of the first cell-center at the coarsest level for which $\rho_0 <$ {\tt base\_cutoff\_density}.
\item In {\tt base\_state}, when we are generating the initial background/base state, if we are above {\tt base\_cutoff\_density\_loc}, just use the values for $\rho,T$, and $p$ at {\tt base\_cutoff\_density\_loc}.
\item In {\tt make\_hgrhs}, we only add the volume discrepancy if $\rho_0 >$ {\tt base\_cutoff\_density}.
\item In {\tt make\_macrhs}, we only add the volume discrepancy if $\rho_0 >$ {\tt base\_cutoff\_density}.
\item In {\tt mkscalforce} subroutine {\tt mkrhohforce}, once $\rho_0 \le$ {\tt base\_cutoff\_density}, we compute $\nabla p_0$ with a difference stencil instead of simply setting it to $\rho_0 g$.
\item In {\tt rhoh\_vs\_t} function {\tt makeRhoHfromP}, the base state pressure at edges is computed differently based on where we are in relation to the {\tt base\_cutoff\_density}.  If we are at a equal or higher density than {\tt base\_cutoff\_density}, we integrate $\rho g$ from the nearest cell-centered $p_0$ value.  If we are at a lower density than {\tt base\_cutoff\_density}, we just use the cell-centered value.
\item In {\tt update\_scal}, if the new $\rho$ is less than {\tt base\_cutoff\_density}, we call the EOS to compute $\rho h$.
\end{itemize}
\section{burning\_cutoff}
\begin{itemize}
\item In {\tt react\_state}, we only call the burner if $\rho >$ {\tt burning\_cutoff\_density}.
\end{itemize}
\end{document}

>>>>

These are working notes for the low density parameters in {\tt MAESTRO}.
\section{anelastic\_cutoff}
\begin{itemize}
\item In {\tt base\_state}, we abort the program if {\tt anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.
\item After we initilize the base state in {\tt varden} and at the beginning of {\tt advance}, We compute the coordinate associated with {\tt anelastic\_cutoff}, {\tt anelastic\_cutoff\_coord}.  This is done by setting ${\tt anelastic\_cutoff\_coord}= r$ as soon as $\rho_0(r) <$ {\tt anelastic\_cutoff}.
\item In {\tt correct\_base}, we only update $\rho_0$ for $r\in[0,{\tt anelastic\_cutoff\_coord}-1]$.
\item In {\tt make\_div\_coeff}, we change how we compute {\tt div\_coeff} at and above ${\tt anelastic\_cutoff\_coord}$.
\item In {\tt make\_psi}, we only compute $\psi$ for $r\in[0,{\tt anelastic\_cutoff\_coord}-1]$.
\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} to zero at and above ${\tt anelastic\_cutoff\_coord}$.
\end{itemize}
\section{base\_cutoff\_density}
\begin{itemize}
\item In {\tt base\_state}, we abort the program if {\tt anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.
\item In {\tt base\_state}, we compute a physical cutoff location, {\tt base\_cutoff\_density\_loc}, which is defined as the physical location of the first cell-center at the coarsest level for which $\rho_0 <$ {\tt base\_cutoff\_density}.
\item In {\tt base\_state}, when we are generating the initial background/base state, if we are above {\tt base\_cutoff\_density\_loc}, just use the values for $\rho,T$, and $p$ at {\tt base\_cutoff\_density\_loc}.
\item After we initilize the base state in {\tt varden} and at the beginning of {\tt advance}, We compute the coordinate associated with {\tt base\_cutoff\_density}, {\tt base\_cutoff\_density\_coord}.  This is done by setting ${\tt base\_cutoff\_density\_coord}= r$ as soon as $\rho_0(r) <$ {\tt base\_cutoff\_density}.
\item In {\tt make\_hgrhs}, we only add the volume discrepancy if $r < {\tt base\_cutoff\_density\_coord}$.
\item In {\tt make\_macrhs}, we only add the volume discrepancy if $r < {\tt base\_cutoff\_density\_coord}$.
\item In {\tt mkscalforce} subroutine {\tt mkrhohforce}, once $\rho_0 \le$ {\tt base\_cutoff\_density}, we compute $\nabla p_0$ with a difference stencil instead of simply setting it to $\rho_0 g$.
\item In {\tt rhoh\_vs\_t} function {\tt makeRhoHfromP}, the base state pressure at edges is computed differently based on where we are in relation to the {\tt base\_cutoff\_density}.  If we are at a equal or higher density than {\tt base\_cutoff\_density}, we integrate $\rho g$ from the nearest cell-centered $p_0$ value.  If we are at a lower density than {\tt base\_cutoff\_density}, we just use the cell-centered value.
\item In {\tt update\_scal}, if the new $\rho$ is less than {\tt base\_cutoff\_density}, we call the EOS to compute $\rho h$.
\end{itemize}
\section{burning\_cutoff}
\begin{itemize}
\item After we initilize the base state in {\tt varden} and at the beginning of {\tt advance}, We compute the coordinate associated with {\tt burning\_cutoff\_density}, {\tt burning\_cutoff\_density\_coord}.  This is done by setting ${\tt burning\_cutoff\_density\_coord}= r$ as soon as $\rho_0(r) <$ {\tt burning\_cutoff\_density}.
\item In {\tt react\_state}, we only call the burner if $\rho >$ {\tt burning\_cutoff\_density}.
\end{itemize}
\end{document}
